Datastorr: a workflow and package for delivering successive versions of ``evolving data'' directly into R

### 2019-03-13 ms.tex
Minor changes requested by journal

%\documentclass[letterpaper]{oup-contemporary}
\documentclass[a4paper,num-refs]{assets/oup-contemporary}

@@

%%% Author Notes
\authnote{\authfn{1}daniel.falster@unsw.edu.au}

@@

\section{Availability of source code and requirements}

@@

@@

\subsection{List of abbreviations}
API = An Application Programming Interface provides a set of protocols for exchanging information. DOI = Digital Object Identifier.

@@

DSF was funded by the Australian Research Council. MWP was funded by a NSERC Discovery Grant.

>>>>

%\documentclass[letterpaper]{oup-contemporary}
\documentclass[a4paper,num-refs]{oup-contemporary}

@@

%%% Author Notes
\authnote{\authfn{1}daniel.falster@unsw.edu.au, +61-2-93858431\\
ORCID IDs. Daniel S Falster: 0000-0002-9814-092X, Matthew  W. Pennell: 0000-0002-2886-3970, William K. Cornwell: 0000-0003-4080-4073
}

@@

\section{Availability of Supporting Data}

Snapshots of the code and example file are archived in the GigaScience GigaDB repository \cite{Falster-2019}.

@@

\begin{itemize}
\item Project name:  \texttt{datastorr example} 
\item Project home page: \smurl{github.com/richfitz/datastorr.example}.
\item Operating system(s): Platform independent
\item Programming language: R
\item License: MIT
\end{itemize}

\begin{itemize}
\item Project name:  \texttt{taxonlookup} 
\item Project home page: \smurl{github.com/traitecoevo/taxonlookup}.
\item Operating system(s): Platform independent
\item Programming language: R
\item License: MIT
\end{itemize}

@@

\subsection{List of abbreviations}
API = An Application Programming Interface provides a set of protocols for exchanging information. 
CKAN = Comprehensive Knowledge Archive Network.
DOI = Digital Object Identifier.
FAIR =  Findable, Accessible, Interoperable, Reusable.
Gb =  Gigabyte.
Mb =  Megabyte.
OKFN = Open Knowledge International.

@@

DSF was funded by the Australian Research Council (FT160100113). MWP was funded by a NSERC Discovery Grant (RGPIN-2017-04590).
